Assessing Ranking Fidelity of Competition Structures via Weighted Mutual Information

### 2025-10-20 CMSAC_presentation/CMSAC_reveal_js.qmd
presentation updates

---
title: "Assessing Ranking Fidelity of Competition Structures via Weighted Mutual Information"
author: "Zach Culp, Josie Peterburs, Dr. Gregory J. Matthews, Dr. Ryan P.A. McShane"
format: 
  revealjs: 
    df-print: paged
editor: visual

---

@@

## Comparing Structures

-   Which competition structure is best at reflecting the true strengths of competitors?

@@

-   **Effectivity**[^2]: Interested in correctly ranking the best competitor as first

@@

@@

-   Decide how many rankings are important
    -   Olympic competition ranks the top 3 competitors
    -   Premier League: top 4 (Champions League) and bottom 3 (Relegation)
-   **Salient ranks**: the ranks that matter
    -   Efficacy: 1 through $n$ matter
    -   Effectivity: 1 is only salient rank

@@

-   Want to quantify how well a structure can accurately order the competitors
-   We will propose a metric that quantifies how effectively different tournament structures convey information about competitors’ true strengths

```{r}
knitr::include_graphics("r_dist.png")
```

@@

right_html <- right_table %>% 
  kable(format = "html", row.names = FALSE) %>% 
  kableExtra::kable_styling(font_size = 24)
```
::: {.columns}
::: {.column width="48%"}
```{r}
#| echo: false
left_html
```
:::
::: {.column width="%48%"}
```{r}
#| echo: false
right_html
```
:::
:::

@@

::: {.columns}
::: {.column width="48%"}
```{r}
#| echo: false
left_html
```
:::
::: {.column width="%48%"}
```{r}
#| echo: false
right_html
```
:::
:::

@@

::: {style="position: relative;"}
::: {.fade-out fragment-index="1"}
```{r out.width="60%", fig.show='hold', fig.align='center'}
knitr::include_graphics("boxed_tournament_comparison_plot.png")
```
:::

::: {.fragment .fade-in fragment-index="1" .fade-out fragment-index="2" style="position: absolute; top: 50%; left: 0; right: 0; transform: translateY(-50%);"}
```{r out.width="60%", fig.show='hold', fig.align='center'}
knitr::include_graphics("tournament_comparison_plot.png")
```
:::

::: {.fragment .fade-in fragment-index="2" style="position: absolute; top: 50%; left: 0; right: 0; transform: translateY(-50%);"}
```{r out.width="60%", fig.show='hold', fig.align='center'}
knitr::include_graphics("tournament_comparison_plot_close.png")
```
:::
:::

>>>>

---
title: "Assessing Ranking Fidelity of Competition Structures via Weighted Mutual Information"
author: "Zach Culp, Josie Peterburs, Dr. Gregory J. Matthews, Dr. Ryan P.A. McShane"
format: 
  revealjs: 
    df-print: paged
editor: visual
---

@@

```{r}
knitr::include_graphics("rhat_dist.png")
```

## Comparing Structures
::: {.incremental}
-   Which competition structure is best?

    -   What is considered "best"?

@@

-   **Effectivity**[^2]: Interested in correctly ranking the best competitor as first
:::

::: {.fragment}
```{r}
knitr::include_graphics("salient bar.png")
```

@@

:::

@@

```{r}
knitr::include_graphics("salient examples.png")
```

-   **Salient ranks**: output ranks of the tournament you want to get correct
    -   Efficacy: 1 through $n$ matter
    -   Effectivity: 1 is only salient rank

@@

-   Want to quantify how well a structure can accurately order the competitors
-   We propose a metric that quantifies how effectively different tournament structures recover the true ranking

@@

right_html <- right_table %>% 
  kable(format = "html", row.names = FALSE) %>% 
  kableExtra::kable_styling(font_size = 24)
```

::::: columns
::: {.column width="48%"}
```{r}
#| echo: false
left_html
```
:::

::: {.column width="%48%"}
```{r}
#| echo: false
right_html
```
:::
:::::

@@

::::: columns
::: {.column width="48%"}
```{r}
#| echo: false
left_html
```
:::

::: {.column width="%48%"}
```{r}
#| echo: false
right_html
```
:::
:::::

@@

:::::: {style="position: relative;"}
::: {.fade-out fragment-index="1"}
```{r out.width="60%", fig.show='hold', fig.align='center'}
knitr::include_graphics("boxed_tournament_comparison_plot.png")
```
:::

::: {.fragment .fade-in .fade-out fragment-index="1" fragment-index="2" style="position: absolute; top: 50%; left: 0; right: 0; transform: translateY(-50%);"}
```{r out.width="60%", fig.show='hold', fig.align='center'}
knitr::include_graphics("tournament_comparison_plot.png")
```
:::

::: {.fragment .fade-in fragment-index="2" style="position: absolute; top: 50%; left: 0; right: 0; transform: translateY(-50%);"}
```{r out.width="60%", fig.show='hold', fig.align='center'}
knitr::include_graphics("tournament_comparison_plot_close.png")
```
:::
::::::
